Reproducibility in Plant Pathology

### 2021-06-24 README.rmd
Update Kaique's middle initial per his preferences
Update pkgdown site

> Sparks, A.H., Del Ponte, E.M., dos Santos Alves, K., Foster, Z., Grünwald, N. (YYYY). _Title of paper_. Name of journal/book <https://doi.org/xxx/xxx>

@@

> Authors, (YYYY). _Title of paper_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

> Sparks, A.H., Del Ponte, E.M., dos Santos Alves, K., Foster, Z., Grünwald, N. (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for 'Status and Best Practices for Reproducible Research In Plant Pathology'_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.5281/zenodo.1250665>

@@

A script, `knit_paper.R`, is located in `analysis/paper/knit_paper.R` that will knit the Word document.

>>>>

> Sparks, A.H., Del Ponte, E.M., Alves, K. S., Foster, Z., Grünwald, N. J. (YYYY). _Reproducibility in plant pathology: where do we stand and a way forward_. Name of journal/book <https://doi.org/xxx/xxx>

@@

> Authors, (YYYY). _Reproducibility in plant pathology: where do we stand and a way forward_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

> Sparks, A.H., Del Ponte, E.M., Alves, K. S., Foster, Z., Grünwald, N. J. (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for 'Status and Best Practices for Reproducible Research In Plant Pathology'_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.5281/zenodo.1250665>

@@

A script, `knit_paper.R`, is located in `analysis/paper/knit_paper.R` that will knit the Word document in a Docker session.
